Fast Sorting on Modern Computers

### 2005-06-15 docs/tech_report/merge.tex
made the thing compile now

\afterpage{
\setcounter{subfigure}{0}
\thispagestyle{empty}
\clearpage
\enlargethispage{14em}
\vspace*{-5em}
\begin{figure}[H]
\begin{changemargin}
\subfigure[]{\includegraphics[scale=0.74]{../counters/algorithm_n-0.eps}}
\subfigure[]{\includegraphics[scale=0.74]{../counters/algorithm_s-0.eps}}
\subfigure[]{\includegraphics[scale=0.74]{../counters/base_mergesort-0.eps}}
\subfigure[]{\includegraphics[scale=0.74]{../counters/double_tiled_mergesort-0.eps}}
\subfigure[]{\includegraphics[scale=0.74]{../counters/double_multi_mergesort-0.eps}}
\subfigure[]{\includegraphics[scale=0.74]{../counters/double_multi_mergesort-1.eps}}
\end{changemargin}
\vspace*{6em}
\caption{Branch prediction performance for mergesorts. All graphs use the same scale.}
\label{Branch prediction performance for mergesorts}
\end{figure}
\newpage
}

>>>>

\sixplot{algorithm_n_0.eps}{algorithm_s_0.eps}{base_mergesort_0.eps}{double_tiled_mergesort_0.eps}{double_multi_mergesort_0.eps}{double_multi_mergesort_0.eps}{mergesorts}
%\afterpage{
%\setcounter{subfigure}{0}
%\thispagestyle{empty}
%\clearpage
%\enlargethispage{14em}
%\vspace*{-5em}
%\begin{figure}[H]
%\begin{changemargin}
%\subfigure[]{\includegraphics[scale=0.74]{../counters/algorithm_n-0.eps}}
%\subfigure[]{\includegraphics[scale=0.74]{../counters/algorithm_s-0.eps}}
%\subfigure[]{\includegraphics[scale=0.74]{../counters/base_mergesort_0.eps}}
%\subfigure[]{\includegraphics[scale=0.74]{../counters/double_tiled_mergesort_0.eps}}
%\subfigure[]{\includegraphics[scale=0.74]{../counters/double_multi_mergesort_0.eps}}
%\subfigure[]{\includegraphics[scale=0.74]{../counters/double_multi_mergesort-1.eps}}
%\end{changemargin}
%\vspace*{6em}
%\caption{Branch prediction performance for mergesorts. All graphs use the same scale.}
%\label{Branch prediction performance for mergesorts}
%\end{figure}
%\newpage
%}

### 2005-06-15 docs/tech_report/quick.tex
made the thing compile now

\section{Predictor results}
\sixplot{base_quicksort-0.eps}{base_quicksort9-0.eps}{cache_quicksort-0.eps}{multi_quicksort-0.eps}{sequential_multi_quicksort-0.eps}{}{base, cache and multi quicksorts and base quicksort9}
\sixplot{base_quicksort1-0.eps}{base_quicksort-0.eps}{base_quicksort5-0.eps}{base_quicksort7-0.eps}{base_quicksort9-0.eps}{}{base quicksort without a median, with median of 3, and with pseudo median of 5, 7 and 9}

>>>>

\section{Predictor results}
\sixplot{base_quicksort_0.eps}{base_quicksort9_0.eps}{cache_quicksort_0.eps}{multi_quicksort_0.eps}{sequential_multi_quicksort_0.eps}{}{base, cache and multi quicksorts and base quicksort9}
\sixplot{base_quicksort1_0.eps}{base_quicksort_0.eps}{base_quicksort5_0.eps}{base_quicksort7_0.eps}{base_quicksort9_0.eps}{}{base quicksort without a median, with median of 3, and with pseudo median of 5, 7 and 9}
